---
title: "Reproducible Research: Peer Assessment 1"
output: 
html_document:
keep_md: true
---


## Loading and preprocessing the data
1. Load the data
```{r}
rawData = read.csv("activity.csv", na.strings = "NA")
```

2. Converting dates
```{r}
rawData$formatDate = as.Date(rawData$date,"%Y-%m-%d")
```
## What is mean total number of steps taken per day?

1. Calculating total number of steps per day
```{r}
steps = aggregate(rawData$steps ~ rawData$formatDate, FUN = sum)
```

2. Histogram of the number of steps per day
```{r}
hist(steps$`rawData$steps`,xlab = "Total number of steps per day",ylab = "Frequency")
```
3. Mean and median of the total number of steps per day
```{r}
meanSteps = mean(steps$`rawData$steps`)
medianSteps = median(steps$`rawData$steps`)
```
The mean of steps per day is: `r meanSteps`.  
The median of steps per day is: `r medianSteps`.  

## What is the average daily activity pattern?

1. Now is shown a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days.

```{r}
library(ggplot2)
averages <- aggregate(x = list(steps = rawData$steps), by = list(interval = rawData$interval), FUN = mean, na.rm = TRUE)
ggplot(data = averages, aes(x = interval, y = steps)) + geom_line() + xlab("5-minute interval") + ylab("average number of steps taken")
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
averages[which.max(averages$steps),]
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
